\section{Related Work}

\AT{I am using subsections right now to keep the related work grouped, but will probably drop them once there's more stuff here.}

\emph{Randoop}~\cite{pacheco2007randoop} is a feedback-driven random test generation tool for Java, though the technique underpinning it is universally applicable; \AT{in fact, we implemented a version of this technique in R as the baseline for our evaluation}.
The technique described in the \emph{Randoop} paper generates sequences of method calls to test classes, and randomly generates arguments for these calls in two ways: for primitives, a random value is selected from a predefined, but user-extensible list, and for reference types a value is selected at random from those which have been seen, and if none are available then {\tt null} is selected.
This technique is effective at generating tests involving non-trivial objects that are built up from a number of method calls, but these are uncommon in data science languages.

\AT{Add quickcheck}

\subsection{Test Generation for Dynamic Languages}

Many of the aforementioned techniques rely on static function parameter types in creating values with which to call a function, and dynamic languages do not have static type information.
For example, \emph{LambdaTester}~\cite{lambdatester} focuses on test generation for higher-order functions in JavaScript; a discovery phase is required to identify which parameters are expected to be callbacks, and all other, non-callback arguments are generated in a similar manner to \emph{Randoop}.
Further work on \emph{Nessie}~\cite{arteca2022nessie} expanded upon the approach presented in \emph{LambdaTester} to generate tests for asynchronous callbacks using sequencing and nesting.
Other work on fuzzing deep-learning libraries in Python~\cite{wei2022free} explicitly cite Python being a dynamic language as a challenge for test generation; an important part of the pipeline in the paper is inferring types for function parameters by running existing code.

\AT{A few disparate things on Python, Alexi has the links.}

\FK{What relates to our work: (1) retrofitting type systems, (2) mining function specifications (dynamic invariants, (3) evaluating type systems?, (4) type systems for R, (4) tracing.}